A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-11-19 index.Rmd
new working title
small changes in build procedure

---
output:
  pdf_document:
    keep_tex: true
    template: sagej_template.tex
bibliography: ["references.bib"]
biblio-style: apa
link-citations: yes
citation_package: biblatex
---

\runninghead{Smith and Wittkopf}

\title{workingtitle}

>>>>

---
output:
  bookdown::pdf_book:
    keep_tex: true
    template: sagej_template.tex
bibliography: ["references.bib"]
biblio-style: apa
link-citations: yes
citation_package: biblatex
---

\runninghead{Cultural Transmission in Bronze Age burial rites}

\title{A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe}
